\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,left=2.5cm,right=2.5cm,bottom=3cm,top=2.5cm]{geometry}
\usepackage[latin1]{inputenc}
\usepackage{amsmath,dsfont,bbm,setspace}
\usepackage[longnamesfirst,nonamebreak]{natbib}
\usepackage{longtable,booktabs,pdfpages}
\usepackage[english]{babel}
\usepackage{eurosym,multirow,hyperref}
\usepackage[refpage]{nomencl}
\usepackage[lastexercise]{exercise}

\hypersetup{
    colorlinks,%
    citecolor=blue,%
    filecolor=black,%
    linkcolor=blue,%
    urlcolor=black}

\newcommand{\Pe}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Lik}{\mathcal{L}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\1}{\mathds{1}}
\newcommand{\ow}{\overline{w}}

%\renewcommand{\labelitemi}{}

\begin{document}
\doublespacing

\title{\textcolor{blue}{Multinomial Choices}}
\maketitle


\begin{Exercise}[title=Data Description]
We consider the data ``margarine" in the library bayesm, which is Household Panel Data on Margarine Purchases. 
A formal description of the data is available \href{https://www.rdocumentation.org/packages/bayesm/versions/3.0-2/topics/margarine}. Provide some descriptive evidence on the data.
\begin{itemize}
\item Average and dispersion in product characteristics.
\item Market share, and market share by product characteristics.
\item Mapping between observed attributes and choices. 
\end{itemize}
\end{Exercise}

\begin{Exercise}[title=First Model]

\begin{itemize}
\item We are interested in the effect of price on demand. Propose a model specification.
\item Write the likelihood and optimize the model.
\item Interpret the coefficient on price. 
\end{itemize}
\end{Exercise}

\begin{Exercise}[title=Second Model]
\begin{itemize}
\item We are interested in the effect of family income on demand. Propose a model specification.
\item Write the likelihood and optimize the model.
\item Interpret the coefficient on family
\end{itemize}
\end{Exercise}

\begin{Exercise}[title=Marginal Effects]
Compute and interpret the marginal effects for the first and second models.
\end{Exercise}

\begin{Exercise}[title=IIA]
In this section, we are interested in testing the properties of IIA. We consider the mixed logit setting. 
\begin{itemize}
\item We are still interested in the effect of price and family income. Write and optimize the likelihood of the mixed logit. Denote by $\beta^f$ the estimated coefficients.
\item Consider an alternative specification, where we remove data from one choice. Estimate this model as well, and denote by $\beta^r$ the estimated parameters.
\item Compute the test statistics:
\begin{equation}
MTT = -2 \left[L_r(\beta^f) - L_r(\beta^r) \right] \sim \chi^2(||\beta^r\\)
\end{equation}
\item Conclude on IIA.
\end{itemize}
\end{Exercise}
\end{document}




