\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,left=2.5cm,right=2.5cm,bottom=3cm,top=2.5cm]{geometry}
\usepackage[latin1]{inputenc}
\usepackage{amsmath,dsfont,bbm,setspace}
\usepackage[longnamesfirst,nonamebreak]{natbib}
\usepackage{longtable,booktabs,pdfpages}
\usepackage[english]{babel}
\usepackage{eurosym,multirow,hyperref}
\usepackage[refpage]{nomencl}
\usepackage[lastexercise]{exercise}

\hypersetup{
    colorlinks,%
    citecolor=blue,%
    filecolor=black,%
    linkcolor=blue,%
    urlcolor=black}

\newcommand{\Pe}{\mathbb{P}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\Lik}{\mathcal{L}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\N}{\mathcal{N}}
\newcommand{\C}{\mathcal{C}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\1}{\mathds{1}}
\newcommand{\ow}{\overline{w}}

%\renewcommand{\labelitemi}{}

\begin{document}
\doublespacing

\title{\textcolor{blue}{OLS and Discrete Choice}}
\maketitle


\begin{Exercise}[title=Data creation]
After setting a seed, construct the following objects
\begin{itemize}
\item X1: vector of 10,000 draws from a uniform distribution with range 1:3.
\item X2: vector of 10,000 draws from a gamma distribution with shape 3 and scale 2
\item X3: vector of 10,000 draws from a binomial distribution with probability 0.3
\item eps: vector of 10,000 draws from a normal distribution with mean 2 and sd 1.
\end{itemize}
Create the variables 
\begin{itemize}
\item Y = 0.5 + 1.2 X1 + -0.9 X2 + 0.1 X3 + eps
\item $ydum = \begin{cases} 1, & \mbox{if } Y>mean(Y) \\ 0, & \mbox{otherwise } \end{cases}$
\end{itemize}
\end{Exercise}

\begin{Exercise}[title=OLS]
\begin{itemize}
\item Calculate the correlation between Y and X1. How different is it from 1.2?
\item We are interested in the outcome of the regression of Y on X where X = (1,X1,X2,X3).
\item Calculate the coefficients on this regression.
\item Calculate the standard errors
\begin{itemize}
\item Using the standard formulas of the OLS.
\item Using bootstrap with 49 and 499 replications respectively.
\end{itemize}
\end{itemize}
\end{Exercise}

\begin{Exercise}[title=Numerical Optimization]
We consider the probit estimation of ydum on X. 
\begin{itemize}
\item Write a function that returns the likelihood of the probit.
\item Implement the steepest ascent optimization algorithm to maximize that likelihood.
\item How different are the parameters from the true parameters?
\end{itemize}
\end{Exercise}

\begin{Exercise}[title=Discrete choice]
We consider the determinants of ydum. 
\begin{itemize}
\item Write and optimize the probit, logit, and the linear probability model. You can use pre-programmed optimization packages.
\item Interpret and compare the estimated coefficients. How significant are they?
\end{itemize}
\end{Exercise}

\begin{Exercise}[title=Marginal Effects]
We consider the determinants of ydum. 
\begin{itemize}
\item Compute the marginal effect of X on Y according to the probit and logit models.
\item Compute the standard deviations using
\begin{itemize}
\item The delta method
\item Bootstrap
\end{itemize}
\end{itemize}
\end{Exercise}



\end{document}




