\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage[breaklinks=true]{hyperref}
%opening
%\title{Econ 613: Research Project}
%\subtitle{Instructions}

\title{
Econ 613: Research Projects \\ 
\begin{large} 
Instructions
\end{large}}
\author{}
\date{}

\doublespacing
\begin{document}

\maketitle

\section*{Overview}

The research project is the culminating activity of Econ 613: Applied Econometrics. The goal is to demonstrate your ability to formulate a research question and apply your econometrics skills. 

\paragraph*{General Steps}

\begin{enumerate}
 \item Draft a written proposal (see proposal guidelines) and submit it before April 1st. 
 \item Upon approval, you have until April 30th to complete the research project. 
 \item Both the proposal and the final project should be available on your github account. 
\end{enumerate}

\newpage
\section*{Proposal Guidelines}
The proposal is intended to outline your research idea and provide a good starting point for developing your final research. The proposal should be one/two pages long with the following information.

\begin{enumerate}
\item Title page and abstract 
\item \textbf{Motivation} A brief background and a concise rationale for the motivation of the analysis. A clear statement of your research question.
\item Very brief literature review. 
\item \textbf{Research Design}: Describe the plan for the research project. Questions about data and econometric models should be addressed. Finally, an identification strategy should be outlined.  
\item Include an outline, which is a plan of the research, including specific dates for conducting data work, estimation, and write-up.  
\end{enumerate}

\newpage
\section*{Final Project}
The final project is a scholarly paper on a topic of your choice. I urge you to invest in Latex, which is the standard writing tool for researchers. The final output should be between 15/20 pages, written in English, free of typos and grammatical errors.\footnote{Please do not ask about spacing!}

\begin{enumerate}
\item Title page and abstract 
\item \textbf{Introduction}
\begin{itemize}
 \item Background and importance
 \item Research question
 \item Brief description of the empirical strategy
 \item Brief description of the findings
\end{itemize}
\item Literature review: cite a couple of papers to situate your work in the general literature.
\item Empirical strategy
\begin{itemize}
 \item Data: Describe the data. Provide some empirical regularities and potentially supports your thesis (tables, figures).
\item Describe your empirical strategy; which empirical model are you using? How are your parameters of interest identified? Which variation do you use in the data?
\end{itemize}
\item Results: Describe your findings and conclude. 
\end{enumerate}

Set aside a least one week to proofread and correct your final manuscript. Ask yourself if your words and thoughts are in line. Check \href{https://app.grammarly.com/}{Grammarly} to correct after yourself.

\end{document}
