\documentclass{beamer}
\setbeamertemplate{navigation symbols}{}
\usepackage[latin1]{inputenc}
\usepackage{setspace,dsfont}
\usepackage{amsmath,amssymb,pdfpages}
\usepackage[longnamesfirst,nonamebreak]{natbib}
\usepackage[english]{babel}
\usepackage{eurosym,multirow,hyperref,cmll}
\usepackage{listings}

\newcommand{\Lik}{\mathcal{L}}
\newcommand{\lau}{\lambda_u}
\newcommand{\wi}{\underline{w}}
\newcommand{\m}{\mathcal{M}}
\newcommand{\wa}{\overline{w}}
\newcommand{\lae}{\lambda_e}
\newcommand{\1}{\mathbb{1}}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\f}{\mathfrak{f}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\V}{\mathbb{V}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Real}{\mathbb{R}}
\newcommand{\X}{\mathcal{X}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\B}{\mathcal{B}}

\hypersetup{
    colorlinks,%
    citecolor=blue,%
    filecolor=blue,%
    linkcolor=blue,%
    urlcolor=blue,
}
%\usetheme{Boadilla}
%\usetheme{Marburg}
%\usetheme{Hannover}
%\usetheme{Pittsburgh}
%\usetheme{umbc1}
\usetheme{Montpellier}
%\usetheme{Singapore}
%\usetheme{}
%\usetheme{}
%\lstset {language=C++}

\DeclareMathOperator{\plim}{plim}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}

\beamersetuncovermixins{\opaqueness<1>{25}}{\opaqueness<2->{15}}
\date{}

\begin{document}
\begin{frame}
\title{ECON 613: Applied Econometrics}
\subtitle{Introduction}
\titlepage
\end{frame}

\frame{\frametitle{Objectives}
\begin{itemize}
\item Present a set of models to understand, evaluate and predict the behaviour of economic agents.
\begin{itemize}
\item Why? 
\item How?
\item What?
\end{itemize}
\item Model Selection.
\item Implementation.
\item Interpretation.
\end{itemize}
}

\frame{\frametitle{Program}
\begin{itemize}
\item Methods
\begin{itemize}
\item Maximum Likelihood Estimation Techniques
\item GMM
\item Numerical Optimization
\item Bootstrap
\end{itemize}
\item Methods for cross section data.
\item Panel data analysis
\item Treatment Evaluation
\item Semiparametric Methods (Time)
\end{itemize}
}

\frame{\frametitle{Method}
\begin{itemize}
\item Final objective is to be able to carry out economic research using a ``commercial", push button software i.e. Stata
\item My objective is to make sure that students understand what goes on behind the black box. As a consequence, you won't be doing any stata before the last two sessions of the class. 
\item Instead econometrics models will be computed using matrix based languages like R and Matlab.
\end{itemize}
}


\frame{\frametitle{Organization}
\begin{itemize}
\item Class time
\item Office hours: Email appointment 
\item TAs:
\begin{itemize}
\item Elessar Chen: elessar.chen@duke.edu
\item Zhangchi Ma: zhangchi.ma@duke.edu
\end{itemize}
\item Questions? 
\end{itemize}
}

\frame{\frametitle{Evaluation (1): Problem sets (individual)}
\begin{itemize}
\item Data Manipulation (R/Stata/...)
\item OLS (Matlab/R)
\item Discrete Choice (Matlab/R)
\item Limited Dependent Variables (Matlab/R)
\item Panel Data (Matlab/R)
\item Recap (Stata)
\end{itemize}
}

\frame{\frametitle{Evaluation (2): Reading notes}
\begin{itemize}
\item Motivation.
\item How: Which models? Which specification? Measurement issues.
\item Findings. Re-interpretation.
\end{itemize}
}

\frame{\frametitle{Evaluation (2): Reading notes (individual)}
\begin{itemize}
\item Gender Gaps in Performance: Evidence from Young Lawyers (Azmat \& Ferrer)
\item Bargaining, Sorting, and the Gender Wage Gap: Quantifying the Impact of Firms on the Relative Pay of Women (Card, Cardoso \& Kline)
\item Children and Gender Inequality: Evidence from Denmark (Kleven, Landais \& Sogaard)
\item Gender Identity, Relative Income Within Households: (Bertrand, Kamenica \& Pan)
\item Selection, Investment, and Women's Relative Wages over Time (Mulligan \& Rubinstein)
\end{itemize}
}

\frame{\frametitle{Evaluation (3): Research Proposal (groups of 2 or 3)}
\begin{itemize}
\item Topic on gender.
\item Ideal data and Model.
\end{itemize}
}


\frame{\frametitle{Details}
\begin{itemize}
\item Github
\item Learn about R and Matlab
\item Reference: A. Colin Cameron and Pravin K. Trivedi (2005), Microeconometrics: Methods and Applications, Cambridge University Press.
\end{itemize}
}


\frame{\tableofcontents[currentsection,hideothersubsections,currentsubsection]}

\section{Methods}
\section{Cross section Analysis}
\section{Panel Data Analysis}
\section{Treatment Evaluation}


\end{document}


